Photovoltaic System Reconfiguration strategy for mismatch condition\\ {\footnotesize \textsuperscript{}}

### 2018-09-02 main.tex
add fig

By inspecting the features of each module in Table \ref{tab1}, there are no configuration for MPP candidate \{0.5A, 0.5A, 2A\} and MPP candidate \{0.5A, 2A, 2A\}. Configuration for MPP candidate \{2A, 2A, 2A\} is that first string include Panel P1, P2 and P4; the second string include Panel P5, P6 and P7; the third string include Panel P3, P8 and P9. Configuration for MPP candidate \{2A, 2A, 3A\} is that first string include Panel P1, P5 and P8; the second string include Panel P3, P4 and P6; the third string include Panel P2, P7 and P9. Optimal configuration for this partial-shading PV array as showed in Fig. \ref{reconfiguration}. 
\begin{figure}%
    \centering
    \subfloat[MPP candidate 3]{{\includegraphics[width=4cm]{mpp3.png} }}%
%    \qquad
    \subfloat[MPP candidate 4]{{\includegraphics[width=4cm]{mpp4.png} }}%
    \caption{Configuration of partial-shading PV array}%
    \label{reconfiguration}%
\end{figure}

@@

\begin{figure}
\centering 
\subfloat[]{
	\label{fig5a}
	\includegraphics[width=5cm]{paper-fig5(a).png} } \\
\subfloat[]{
	\label{fig5b}
	\includegraphics[width=4cm]{mpp3.png} }
\subfloat[]{
	\label{fig5c}
	\includegraphics[width=4cm]{mpp4.png}} \\
\caption{The PV system under shading scenario (a) before reconfiguration, (b) after reconfiguration for MPP candidate \{2, 2, 2\} and (c) MPP candidate \{2, 2, 3\}} 
\end{figure}

@@

As shown, working module on each string are large or equal than required \textit{$Q_{M_n}$}, which means mismatched power loss are minimized. The \textit{P-V} curve for this PV array before and after reconfiguration are showed in Fig.\ref{fig6}. It can be seen that after reconfiguration maximum power (!!!!!!!!!! W and !!!!!!W) are significantly higher than before reconfiguration maximum power (!!!!!!!!W).

\begin{figure}[htbp]
\centerline{\includegraphics[width=5cm]{fig2.png}}
\caption{The \textit{P-V} curves for the PV system under first shading scenario before and after reconfiguration.}
\label{fig6}
\end{figure}

>>>>

By inspecting the features of each module in Table \ref{tab1}, there are no configuration for MPP candidate \{0.5A, 0.5A, 2A\} and MPP candidate \{0.5A, 2A, 2A\}. Configuration for MPP candidate \{2A, 2A, 2A\} is that first string include Panel P1, P2 and P4; the second string include Panel P5, P6 and P7; the third string include Panel P3, P8 and P9. Configuration for MPP candidate \{2A, 2A, 3A\} is that first string include Panel P1, P5 and P8; the second string include Panel P3, P4 and P6; the third string include Panel P2, P7 and P9. Optimal configuration for this partial-shading PV array as showed in Fig. \ref{reconfiguration}. 
\begin{figure}%
    \centering
    \subfloat[MPP candidate 3]{{\includegraphics[width=4cm]{MPP3.png} }}%
%    \qquad
    \subfloat[MPP candidate 4]{{\includegraphics[width=4cm]{MPP4.png} }}%
    \caption{Configuration of partial-shading PV array}%
    \label{reconfiguration}%
\end{figure}

@@

\begin{figure}
\centering 
\subfloat[]{
	\label{fig5a}
	\includegraphics[width=5cm]{paper-fig5(a).png} } \\
\subfloat[]{
	\label{fig5b}
	\includegraphics[width=4cm]{MPP3.png} }
\subfloat[]{
	\label{fig5c}
	\includegraphics[width=4cm]{MPP4.png}} \\
\caption{The PV system under shading scenario (a) before reconfiguration, (b) after reconfiguration for MPP candidate \{2, 2, 2\} and (c) MPP candidate \{2, 2, 3\}} 
\end{figure}

@@

As shown, working module on each string are large or equal than required \textit{$Q_{M_n}$}, which means mismatched power loss are minimized. The \textit{P-V} curve for this PV array before and after reconfiguration are showed in Fig.\ref{fig6}. It can be seen that after reconfiguration maximum power (283 W and 276W) are higher than before reconfiguration maximum power (277W).

\begin{figure}[htbp]
\centerline{\includegraphics[width=8cm]{zhao.pdf}}
\caption{The \textit{P-V} curves for the PV system under first shading scenario before and after reconfiguration.}
\label{fig6}
\end{figure}
